Titeltext

### 2018-07-26 thesis/paper/paper.tex
Added one-of

>>>>

\subsection{One-of (Q21510859)}
The one-of constraint limits the values a property may use to a set of given values.

\begin{table}[H]
\caption{One-of constraint (Q21510859)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & constrained statement \\
\hline
Qualifiers & \makecell{allowed values (P2305) -- 1..* \\ values that may be used in the constrained statement} \\
\hline
Violation & \makecell{constrained statement with a value unequal to all allowed values} \\
\hline
Dependency & constrained statement \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

Modelling the one-of constraint requires a rule finding a tripleEDB with the constrained property whose value is unequal to all allowed values, meaning the inequality between each value of constrained statements and all allowed values must be given.
